Approval and participation indexes for a voting process

### 2015-04-23 ApresentacoesArtigos/collectiveRanking/paper.tex
pequena correcao no titulo de escrito sobre indices

\title{Approval and participation index for a voting process} % For titles, only capitalize the first letter

@@

\begin{abstract}
In finding the adequate way to prioritize proposals, the Brazilian participation community agreed about a approval index and a participation index.
Both practice and literature is constantly handled by the experts involved, and the formalization of such model and indexes seem novel.
Beyond innovation, the relevance of this report relies in the nearby use of these indexes to raise and prioritize proposals about public health care in open processes and assist public managers.
\end{abstract}

>>>>

\title{Approval and participation indexes for a voting process} % For titles, only capitalize the first letter

@@

\begin{abstract}
In finding the adequate way to prioritize proposals, the Brazilian participation community agreed about an approval index and a participation index.
Both practice and literature is constantly handled by the experts involved, and the formalization of such model and indexes seem novel.
Beyond innovation, the relevance of this report relies in the nearby use of these indexes to raise and prioritize proposals about public health care in open processes and assist public managers in federal initiatives.
\end{abstract}
